A Motion Blur Resilient Fiducial For Quadcopter Imaging

### 2014-06-15 WACV/paper.tex
Proof-reading changes

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene. A variety of fiducials have
been proposed~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}
in the literature.  These take the form of binary codes arranged into
rectangular grids~\cite{ARToolkit02,Fiala05} or other geometric
primitives arranged in predefined spatial
patterns~\cite{NaimarkF02,Pitag13,runetag11}.  Figure \ref{fig:teaser}
shows the popular ARTag \cite{Fiala05} fiducial as possibly seen from
a quadcopter. A problem for existing fiducials is that low-cost
quadcopters often exhibit very quick and erratic physical movements
that result in motion blur in the captured images from the quadcopter's onboard
camera. This motion blur has an adverse effect on the recognition of fiducial
markers. This can be seen in Figure \ref{fig:teaser}--(b) where the
ARTag fiducial cannot be recognized due to motion blur. This is not
too surprising as most existing fiducials are not designed to handle
motion blur.

@@

Qualitatively we see in Figure~\ref{fig:blur_maximum} that despite of
even more blur than earlier described (50 units or more) detection is
still feasible and practical.  Quantitatively, the comparison of
recognition rate is shown in Figure~\ref{fig:recognition_rate}.
Even under more severe blur, of 65 pixels, the algorithm is
successful.  Our recognition is 100\% for all codes except the ``00''
which is undetectable after 50 pixels blur (which is still
significantly better than ARTag).  Reasons for the lower performance
when``00'' tags are present is discussed in
Section~\ref{sec:discussion}.

@@

We also compared results on the recorded feed using the AR Drone
quadcopter. In our experimental setup, we have placed two ARTags in
the scene along with our fiducial to compare the resilience of blur by
each fiducial type. We have used ar\_track\_alvar, ROS Wrapper for the
ALVAR library~\cite{ros_alvar}, to detect the ARTags from the stream
captured with the quadcopter camera. In each test dataset, we have
used different two bit binary coded fiducial and recorded video of
around two minute duration (i.e., around 1000 frames).  The quadcopter
was flown in a routine manner in the room with its camera facing the
wall (see supplementary videos). The comparison of the recognition
rate is shown in Table~\ref{tab:recognition_accuracy}. Recognition
rate of our fiducials ranges from 86.5\% to 94.1\%, while the ARTag is
60.3\% to 65.6\%.  Classification accuracy of all fiducials (ARTag as
well as ours) was approximately 100\%, i.e., when tags were detected
they were the correct fiducials and not other objects in the scene.

@@

In another setup we arranged our fiducials on four sides of a box and
revolved the quadcopter around the box. Later, we repeated the process
by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
frames from this sequence as well as the performance of both
fiducials. The overall detection rate of our tags is 90\% while that
of ARTags is only around 60\%.

>>>>

In order to be effective, fiducial markers (or simply, fiducials) need
to be easily detected in the scene. A variety of fiducials have
been proposed~\cite{NaimarkF02,ARToolkit02,Fiala05,Pitag13,runetag11}
in the literature.  These take the form of binary codes arranged into
rectangular grids~\cite{ARToolkit02,Fiala05} or other geometric
primitives arranged in predefined spatial
patterns~\cite{NaimarkF02,Pitag13,runetag11}.  Figure \ref{fig:teaser}
shows the popular ARTag \cite{Fiala05} fiducial as possibly seen from
a quadcopter. A problem for existing fiducials is that low-cost
quadcopters often exhibit very quick and erratic physical movements
that result in motion blur evidenced in the images captured from the quadcopter's onboard
camera. This motion blur has an adverse effect on the recognition of fiducial
markers. This can be seen in Figure \ref{fig:teaser}--(b) where the
ARTag fiducial cannot be recognized due to motion blur. This is not
too surprising as most existing fiducials are not designed to handle
motion blur.

@@

Qualitatively, we see in Figure~\ref{fig:blur_maximum} that despite of
even more blur than earlier described (50 units or more), detection is
still feasible and practical.  Quantitatively, the comparison of
recognition rate is shown in Figure~\ref{fig:recognition_rate}.
Even under more severe blur, of 65 pixels, the algorithm is
successful.  Our recognition is 100\% for all codes except the ``00''
which is undetectable after 50 pixels blur (which is still
significantly better than ARTag).  Reasons for the lower performance
when``00'' tags are present, is discussed in
Section~\ref{sec:discussion}.

@@

We also compared results on the recorded feed using the AR Drone
quadcopter. In our experimental setup, we have placed two ARTags in
the scene along with our fiducial to compare the resilience of blur by
each fiducial type. We have used ar\_track\_alvar, ROS Wrapper for the
ALVAR library~\cite{ros_alvar}, to detect the ARTags from the stream
captured with the quadcopter camera. In each test dataset, we have
used different two bit binary coded fiducial and recorded video of
around two minute duration (i.e., around 1000 frames).  The quadcopter
was flown in a routine manner in the room with its camera facing the
wall. The comparison of the recognition
rate is shown in Table~\ref{tab:recognition_accuracy}. Recognition
rate of our fiducials ranges from 86.5\% to 94.1\%, while the ARTag is
60.3\% to 65.6\%.  Classification accuracy of all fiducials (ARTag as
well as ours) was approximately 100\%, i.e., when tags were detected
they were the correct fiducials and not other objects in the scene.

@@

In another setup we arranged our fiducials on four sides of a box and
revolved the quadcopter around the box (see the supplementary video). Later, we
repeated the process by replacing our fiducial by ARTags. Figure~\ref{fig:setup} shows some
frames from this sequence as well as the performance of both
fiducials. The overall detection rate of our tags is 90\% while that
of ARTags is only around 60\%.
